Realizability-Preserving DG-IMEX Method for the Two-Moment Model of Fermion Transport \tnoteref{support}

### 2018-06-20 Documents/M1/realizableFermionicM1/sections/imex.tex
Modifications to definition of PD-IMEX

\subsection{Diffusion Accurate, Positivity-Preserving IMEX Schemes}

@@

We then seek to design GSA IMEX schemes of Type~ARS conforming to the following definition

@@

  A diffusion accurate, positivity-preserving IMEX scheme satisfies the following properties

@@

@@

@@

    \item Positivity-preserving (conditions given by \cite{hu_etal_2018}; with $c_{\mbox{\tiny Sch}}>0$ and maximal).

@@

>>>>

\subsection{Positivity-Preserving, Diffusion Accurate IMEX Schemes}

@@

We then seek to design IMEX schemes of Type~ARS conforming to the following working definition

@@

  Let PD-IMEX be a consistent, positivity-preserving, diffusion accurate, and low-stage GSA IMEX scheme satisfying the following properties

@@

    \item Consistency of the implicit coefficients
      \sum_{i=1}^{s}w_{i}=1.

@@

    \item Positivity-preserving (conditions given by \cite{hu_etal_2018}; with $c_{\mbox{\tiny Sch}}>0$).

@@

@@

    \item Globally stiffly accurate (GSA)
      a_{si}=w_{i}\quad\text{and}\quad\tilde{a}_{si}=\tilde{w}_{i},\quad i=1,\ldots,s.
